---
title: "R Exercises Session 8"
author: "Vanson Lee"
date: "Thursday, June 27, 2019"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Create a `Header2` header below with the name "Answer 1".

## Answer 1

2. Add an unordered list (in Markdown syntax) of your favorite food dishes and
add their ingredients as sub-items in the list. You should enter at least two
dishes with two ingredients each.

*Kimchi Fried Rice
   + Rice
   + Kimchi
   + Butter
   + Porkbelly
   + Korean BBQ Sauce
   + Egg

*Sweet Potato Hash
   + Sweet Potato
   + Butter
   + Eggs
   + Bacon
   + Peppers
   + Cheese

3. Add an R code chunk below. Show the `summary` of the `Orange` dataset. Run a
linear regression using the `lm` function to predict `circumference` from `age`
and assign the result. Show the `summary` of the fit object that you assigned. 

```{r}

data(Orange)
summary(Orange)
circumference.lm <- lm(circumference ~ age, data=Orange)
circumference.lm
summary(circumference.lm)
orangep<- predict(circumference.lm, data.frame(age=100), interval = "predict")
orangep
summary(orangep)
```

4. Add a link below (_in RMarkdown format_) to your favorite R reference website.

[R Studio](https://wwww.rstudio.com)

5. Replace the author field in the `yaml` header with your name and `knit` the
RMarkdown document into a Word document (make sure that the document 'knits').
First clone the `CUNYSPHcode/IntroR_FinalAssignment` onto your GitHub account.
Then, create a pull request on GitHub with the **modified** RMarkdown file. 

